### 2014-06-04 writing/S'14 paper/intro.tex
First proof of intro and methods

In our experiments, we use this pre-specified logical grammar to
generate controlled data sets encoding the semantic relationships
between pairs of expressions and evaluating whether each of two
classes of neural model --- plain RNNs and recursive neural tensor
networks (RNTNs, \cite{socher2013acl1}) --- can learn those
relationships correctly. In our first experiment
(Section~\ref{sec:join}), we evaluate the ability of these models to
learn the core relational algebra of natural logic from data. Our
second experiment (Section~\ref{sec:recursion}) extends this
evaluation to cover relations between complex recursive structures
like $(a \plor b)$ and $\plneg(\plneg a \pland \plneg b)$, and our
third experiment (Section~\ref{sec:quantifiers}) involves relations
between quantified statements like `every reptile walks' and `every
turtle moves'. We find that the plain RNN achieves only mixed results
in all three experiments, whereas the stronger RNTN models generalized
well in every case, suggesting that it has in fact learned, or at
least learned to simulate, our target logical
concepts. % TODO: Update with current results

>>>>

In our experiments, we use this pre-specified logical grammar to
generate controlled data sets encoding the semantic relationships
between pairs of expressions and evaluating whether each of two
classes of neural model --- plain RNNs and recursive neural tensor
networks (RNTNs, \cite{socher2013acl1}) --- can learn those
relationships correctly. In our first experiment
(Section~\ref{sec:join}), we evaluate the ability of these models to
learn the core relational algebra of natural logic from data. Our
second experiment (Section~\ref{sec:recursion}) extends this
evaluation to cover relations between complex recursive structures
like $(a \plor b)$ and $\plneg(\plneg a \pland \plneg b)$, and our
third experiment (Section~\ref{sec:quantifiers}) involves relations
between quantified statements like \ii{every reptile walks} and \ii{every
turtle moves}. We find that the plain RNN achieves only mixed results
in all three experiments, whereas the stronger RNTN models generalized
well in every case, suggesting that it has in fact learned, or at
least learned to simulate, our target logical
concepts. % TODO: Update with current results

### 2014-06-04 writing/S'14 paper/methods.tex
First proof of intro and methods

We study neural models that adhere to the linguistic \ii{principle of
  compositionality}, which says that the meanings for complex
expressions are derived from the meanings of their constituent parts
via specific combination functions \cite{Partee84,Janssen97}. In our
distributional model, word meanings are vectors of length $N$. The
combination function concatenates pairs of them to form vectors of
length $2N$ and maps those larger vectors back into length $N$
vectors, which can then be merged again to create more complex
phrases. Once the entire sentence-level representation has been
derived, it fed to a classifier trained in a supervised manner.

@@

For a composition layer, we evaluate models with both the plain neural
network layer function (eq.~\ref{rnn}) and the RNTN layer function
proposed in \citet{chen2013learning} (eq.~\ref{rntn}). A sigmoid
nonlinearity (element-wise $\tanh$) is applied to the output of either
layer function, following \cite{socher2013acl1}.
%
\begin{gather} \label{rnn}
y_{\textit{RNN}} = f(\mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + b_i)\\ % TODO: Add column vectors?
\label{rntn}
y_{\textit{RNTN}} = f(\vec{x}^{(l)T} \mathbf{A}^{[1 \ldots N]} \vec{x}^{(r)} + \mathbf{B} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{c})
\end{gather} % TODO: Explain third order tensor parameter?
%
Here, the $l$ and $r$ superscripts indicate the vector representations
for the left and right children of the local structure interpreted as
$y$. The RNN concatenates them, multiplies them by an $N \times 2N$
matrix of learned weights, and applies the element-wise non-linearity
to the resulting vector (plus a bias term). The RNTN has the same
basic structure, but with the addition of a tensor $\mathbf{A}$,
dimension $2N \times N \times N$, modeling interactions between the
child vectors.

The comparison layer uses the same type function template as the
composition function (either an NN layer or an NTN layer) with
independantly learned parameters and a separate nonlinearity function.
Rather than use a $\tanh$ nonlinearity here, we found a substantial
improvement in performance by using a rectified linear function for
$f_{b}$. In particular, we use the leaky rectified linear function
\cite{maasrectifier}: $f_{b}(\vec{x})=\max(\vec{x}, 0) +
0.01\min(\vec{x}, 0)$, applied element-wise.

>>>>

We study neural models that adhere to the linguistic \ii{principle of
  compositionality}, which says that the meanings for complex
expressions are derived from the meanings of their constituent parts
via specific combination functions \cite{Partee84,Janssen97}. In our
distributed setting, word meanings are vectors of length $N$. The
combination function concatenates pairs of them to form vectors of
length $2N$ and maps those larger vectors back into length $N$
vectors, which can then be merged again to create more complex
phrases. Once the entire sentence-level representation has been
derived, it fed to a classifier trained in a supervised manner.

@@

For a composition layer, we evaluate models with both the plain neural
network layer function \eqref{rnn} and the RNTN layer function
proposed in \citet{chen2013learning} \eqref{rntn}. A sigmoid
nonlinearity (element-wise $\tanh$) is applied to the output of either
layer function, following \cite{socher2013acl1}.
%
\begin{gather} \label{rnn}
y_{\textit{RNN}} = f(\mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{b}) \\ % TODO: Add column vectors?
\label{rntn}
y_{\textit{RNTN}} = f(\vec{x}^{(l)T} \mathbf{A}^{[1 \ldots N]} \vec{x}^{(r)} + \mathbf{B} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{c})
\end{gather} % TODO: Explain third order tensor parameter?
%
Here, the $l$ and $r$ superscripts indicate the vector representations
for the left and right children of the local structure interpreted as
$y$. The RNN concatenates them, multiplies them by an $N \times 2N$
matrix of learned weights, and applies the element-wise non-linearity
to the resulting vector (plus a bias term). The RNTN has the same
basic structure, but with the addition of a tensor $\mathbf{A}$,
dimension $N \times N \times N$, modeling interactions between the
child vectors.

The comparison layer uses the same kind of function template as the
composition function (either an NN layer or an NTN layer) with
independently learned parameters and a separate nonlinearity function.
Rather than use a $\tanh$ nonlinearity here, we found a substantial
improvement in performance by using a rectified linear function for
$f_{b}$. In particular, we use the leaky rectified linear function
\cite{maasrectifier}: $f_{b}(\vec{x})=\max(\vec{x}, 0) +
0.01\min(\vec{x}, 0)$, applied element-wise.
